\section*{Motivation}
Our work in poems classification problem proposed with a lot of new methods and techniques. In this paper we are target to acheive the human experts performance to classify the poems which is not presented in such way or  performance before. 
\begin{itemize}
\item  We introduced Poem classifications as a deep learning problem, not an algorithmic problem nor rule-based to utilize the feature in a poem that it is a sequence of character and how can we apply RNN with LSTM to classify it.
  \begin{enumerate}
    \item The size of the dataset for each encoding.
    \item The learning curve and the time is taken to learn the problem.
    \item Classification performance results: The results we got into this paper is not achieved into any of the previous work in this field before with the variety of options or in machine learning techniques.

    \item Runtime performance.
  \end{enumerate}

\item We used different hyperparameters for each data encoding and provide comparative study based on our experiments.
\item We worked on big datasets which are not represented by such amount of data before to show the effect and provide accurate and reliable results for our models.
\item Our data was not balanced so, we introduce how we solve this problem using custom weighted loss function and also, compare it with the normal one. Moreover, we tried to remove the small classes to check the effect on the total accuracy for the RNN model. All the above experiments provided with comparative study and performance recommendation results.
\item We applied the same techniques to the Arabic and English and provided the experiments results for both and show how we can apply it to any other language and text in general.
  
\end{itemize}

% NOTE: The question your paper should answer.
%% Question is What is the new in this paper?
% NOTE: A brief review of the literature used and your arguments on the topic. You can review the theory and prove your awareness of the evidence and arguments.
% NOTE: State what your explanation and arguments will be.
% NOTE: An explanation of how your ideas differ from the positions of other authors.
% NOTE: A short outline of the parts of the paper.
% NOTE: As in the case with a social issues essay, and as seen in a motivation essay example, the writer should present short bibliography including interviews, databases, online directories, etc.
% NOTE: The research proposal on motivation should be informative – high quality is of primary concern when writing this type of paper. Writing 3-4 pages will be enough. The more effort you put into writing the better the estimation of your reader will be. The more detail you include in your research proposal the more useful it will be.
